---
title: "Leaderboard & Entries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Leaderboard & Entries}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(draft.kings)
```

# Analyzing Contest Results and Rankings

## dk_get_leaderboard()

*Get player leaderboard information for a particular contest*

The `dk_get_leaderboard()` function retrieves comprehensive information about the participants and their performance in a specific DraftKings contest. This includes:

1. A list of all entries in the contest
2. Fantasy points scored by each entry
3. User information associated with each entry
4. Current rank of each entry
5. Winnings (if any) for each entry

This data allows for in-depth analysis of contest results, participant performance, and payout distributions. It's particularly useful for understanding successful strategies, identifying top users, and gaining insights into contest dynamics.

```{r}
dk_get_leaderboard(contest_key = 133645678) 
```

>**Note:**
> Some functions such as `dk_get_leaderboard()` require passing the session cookies to the
> function as a JSON file.

## dk_get_entries()

*Get entries for a contest*

Retrieve detailed information about specific entry rosters in a contest, including:

1. The complete drafted roster for each entry
2. Detailed statistics for every player in an entry's roster
3. Fantasy points earned for each statistical category
4. Performance breakdowns and scoring details
5. Any late swap or substitution information
6. Entry metadata such as entry fees, potential winnings, and current ranking

This function provides a deep dive into the composition and performance of individual contest entries, allowing for  analysis of roster strategies and player contributions.

```{r}
dk_get_entries(draft_group_id = 80584, entry_keys = c(3618408508, 3618897002))
```

>**Note:**
> An entry key is a numeric (or character) key that corresponds to a specific entry in a specific contest. See output from `dk_get_leaderboard()`.